An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
typo fixed
fished out a couple more of the scales. Lots more there.

The section "Implementation" will go through the algorithm and show how to use the "CMPS" package. An further example that illustrates the main points are also included. The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44. And the last section covers some final discussion and conclusions.

@@

        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level. \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.

@@

While `cmps_signature_plot()` focuses on the signature level,  `cmps_segment_plot()` focuses on the segment level. It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.  When checking `sig.plot$seg_shift` we notice that  segment number 6 is not one of the congruent matching profile segments. We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position). 
Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.

*   \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at scale one (its original scale). Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at scale one, and segment 6 at scale one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment scale; the blue dashed lines show the tolerance zone around the green dashed line. We can see here none of the five highest peaks at scale one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at scale one}
\end{figure}

Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment scales together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.

>>>>

The section "Implementation" will go through the algorithm and show how to use the "CMPS" package. A further example that illustrates the main points are also included. The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44. And the last section covers some final discussion and conclusions.

@@

        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level. \autoref{fig:seg_all} shows an example of 3 levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.

@@

While `cmps_signature_plot()` focuses on the signature level,  `cmps_segment_plot()` focuses on the segment level. It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.  When checking `sig.plot$seg_shift` we notice that  segment number 6 is not one of the congruent matching profile segments. We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:

*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (the top level). We used  `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score. Therefore the top five peaks are identified in the cross-correlation curve at level one. Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`. The solid black line shows the segment at its original position (which in this example is very close to the actual registration position).

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at level 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}

Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
